---
csl: PCE.csl
bibliography: ~/GitHub/BeeLabR/BibTex/Full.bib
header-includes:
  - \usepackage{zxjatype} # 日本語を使う
  - \setjamainfont{Hiragino Mincho Pro} # 日本語フォント
  - \setmainfont{Times} 
  - \usepackage{fouriernc} # 立体のギリシア文字など
  - \usepackage{lscape} # 図を回転する
  - \usepackage{setspace} # 行間の調節
  - \setstretch{2.5}
  - \setlength\parskip{0pt} #段落間間隔
  - \usepackage{lineno} # 行番号を追加するためのパッケージ
  - \usepackage{color, caption} # フォントカラー
  # - \pagestyle{empty}
output:
  pdf_document:
    latex_engine: xelatex
    fig_caption: TRUE
    number_sections: FALSE
---


```{r setup, echo = F, message = F, warning = F}
# 念のため、全オブジェクトを除去
rm(list = ls())

main_path <- "~/XXX/main.rmd"
sup_path <- "~/XXX/supplemental.rmd"

eval_fig <- T

TITLE <- "my title"
RUNING_TITLE <- "short title"
AUTHOR <- "Keach Murakami^1^"
AFFILIATIONS <- "^1^Graduate School of Agricultural and Life Sciences, The University of Tokyo"
ADDRESS <- "^1^Yayoi, Bunkyo, Tokyo, 113--8657, Japan"
MAIL <- "keach.murakami@gmail.com"

devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/TeX_accessory.R")
devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/ggplot_accessory.R")
devtools::source_url("https://raw.githubusercontent.com/KeachMurakami/Sources/master/Startup_silent.R")


fig_prefix <- c("Fig.", "Fig.")
fig_ref <-
  function(fig_label, prefix = T){
    fig_num <- length(fig_label)
    if(!prefix) fig_prefix <- c("", "")
    
    if(fig_num == 1){
      paste0(fig_prefix[1], " \\ref{fig:", fig_label, "}")
    } else {
      paste0(" \\ref{fig:", fig_label, "}") %>%
      str_c(., collapse = ",") %>%
      paste0(fig_prefix[2], .)
    }
  }

table_prefix <- c("Table", "Table")
table_ref <-
  function(table_label, prefix = T){
    table_num <- length(fig_label)
    if(!prefix) fig_prefix <- c("", "")
    
    if(table_num == 1){
      paste0(table_prefix[1], " \\ref{table:", table_label, "}")
    } else {
      paste0(" \\ref{table:", table_label, "}") %>%
      str_c(., collapse = ",") %>%
      paste0(table_prefix[2], .)
    }
  }

knitr::opts_chunk$set(echo = FALSE, fig.width = 5, fig.height = 5, dpi = 400,
                      message = FALSE, warning = FALSE, cache = F, eval = T)


Eqn_Eq <- c("Eqn", "Eqns")
```


- Title:
    - `r TITLE`
- Running title:
    - `r RUNING_TITLE`
- Authors:
    - `r AUTHOR`
- Affiliation:
    - `r AFFILIATION`
- Address:
    - `r ADDRESS`
- E-mail:
    - `r MAIL`

\newpage

\linenumbers

**Abstract**

------

**Keywords**

------

**Abbreviations**


\newpage

\captionsetup[figure]{labelsep=period, name=Fig.}
\captionsetup[table]{labelsep=none, name=Table}


```{r child = main_path}
```

\newpage
\noindent  
**Author contributions**  


\noindent  
**Acknowledgements**  
This work was supported by JSPS KAKENHI Grant Number 26·9372 to KM.



\setcounter{table}{0}
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}

```{r child = sup_path}
```


\newpage  
\noindent  

\listoffigures
\listoftables

**References**  